The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
fix typos

We altered social scale based on visual (short distance) and auditory (long
distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
the spatial distance threshold required for group assignment (see above) and
re-assigned groups at incremental distance between 5-500m. For example, at the
finest social scale, only individuals within 5m of one another were considered
in the same group, whereas at the coarsest social scale, individuals within 500m
of one another were considered in the same group.

@@

We altered the temporal scale of mutlilayer networks using a moving time-window
approach to define seasons.

@@

**Observational scale** <!--(temorary header)-->: Studies of social network analysis
vary in the number and frequency of observations as well as the data collection
technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
2019).

@@

* Neighbors: number of unique individuals adjacent to each actor. Considered in
a single layer, this is equal to the degree.

* Neighborhood: number of unique individuals across all layers. High
neighborhood = a high number of unique individuals connected to an actor.

* Relevance: layer centric metric, corresponding to the number of neighbors on a
layer divided by the total neighborhood for each actor. High relevance means
that the layer is highly relevant to the individuals connections. A low
relevance means this layer does not contribute many neighbors to an individuals
overall neighborhood.

* Connective redundancy: the total multilayer neighborhood divided by the
multidegree. High connective redundancy indicates a multilayer network that has
many repeated edges across layers between an actor and its neighbours. Low
connective redundancy indicates that each layer is important for preserving all
social ties.

* Layer similarily: how similar each layer is (Brodka 2018). Pearson's
correlation coefficient of degree vectors for each layer, comparing each
landcover across seasons.

@@

(ref:lcres) varying scale in landcover resolution. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), ultilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance and D) mean graph strength across individuals showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.

@@

(ref:winlen) varying scale in time window length. For each time windown length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:nobs) varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete dataset to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.

@@

(ref:winpos) varying scale in time window position. For each time windown position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.

>>>>

We altered social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified
the spatial distance threshold required for group assignment (see above) and
re-assigned groups at incremental distance between 5-500m. For example, at the
finest social scale, only individuals within 5m of one another were considered
in the same group, whereas at the coarsest social scale, individuals within 500m
of one another were considered in the same group.

@@

We altered the temporal scale of multilayer networks using a moving time-window
approach to define seasons and

@@

**Observational scale** <!--(temporary header)-->: Studies of social network analysis
vary in the number and frequency of observations as well as the data collection
technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
2019).

@@

* Neighbours: number of unique individuals adjacent to each actor. Considered in
a single layer, this is equal to the degree.

* Neighbourhood: number of unique individuals across all layers. High
neighbourhood = a high number of unique individuals connected to an actor.

* Relevance: layer centric metric, corresponding to the number of neighbours on a
layer divided by the total neighbourhood for each actor. High relevance means
that the layer is highly relevant to the individuals connections. A low
relevance means this layer does not contribute many neighbours to an individuals
overall neighbourhood.

* Connective redundancy: the total multilayer neighbourhood divided by the
multidegree. High connective redundancy indicates a multilayer network that has
many repeated edges across layers between an actor and its neighbours. Low
connective redundancy indicates that each layer is important for preserving all
social ties.

* Layer similarity: how similar each layer is (Brodka 2018). Pearson's
correlation coefficient of degree vectors for each layer, comparing each
landcover across seasons.

@@

(ref:lcres) varying scale in landcover resolution. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance and D) mean graph strength across individuals showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions.

@@

(ref:winlen) varying scale in time window length. For each time window length (of a sequence from 40 to 100 by 5), multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau around 0.65 before decrease between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers remained consistently sparse.

@@

(ref:nobs) varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for lichen and open. B) Mean connective redundancy across individuals increased with increasing number of observations, with a decreasing rate of increase around 100 observations. C) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. D) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained sparse throughout for summer layers.

@@

(ref:winpos) varying scale in time window position. For each time window position (of a sequence from 1 to 48), the time window used to define seasons was shifted and multilayer networks were constructed for each landcover class (open, forest and lichen) across two seasons (winter and summer) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers. C) Mean layer relevance decreased for winter layers and increased for summer layers, showing greater connectivity in summer layers at later window positions. D) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers.
